### 2022-12-12 paper3.tex
formatting

Taken together, we obtain the design prior
$\theta \given \hat{\theta}_{o}, \sigma^{2}_{o} \sim \Nor(\hat{\theta}_{o}, \sigma^{2}_{o})$
for self-replications and the design prior
$\theta \given \hat{\theta}_{o}, \sigma^{2}_{o} \sim \Nor(\hat{\theta}_{o}, \sigma^{2}_{o} + \tau^{2})$
with $\tau^{2} = 0.05^{2}$ for external-replications. For
example, for the experiment ``Labels'', the design prior would be
centered around the original effect estimate
$\hat{\theta}_{o} = 0.205$ with variance
$\sigma^{2}_{o} = 0.05^{2}$ for a
self-replication, and with variance
$\sigma^{2}_{o} + \tau^{2} = 0.05^{2} + 0.05^{2} \approx 0.07^{2}$
for an external-replication. Figure~\ref{fig3:dpexample} (dark-gray solid lines)
shows the densities of the two priors.
% Note that power
% calculations under the former prior have been termed ``predictive power''
% \citep{Micheloud2020}, while the latter prior has not appeared in the SSD for
% replication studies literature.

@@

\subsection{Probability of replication success and required sample size}
To compute the probability of replication success one needs to select an
analysis method and integrate the predictive distribution~\eqref{eq3:fthetar}
% , respectively, \eqref{eq3:zr}
over the associated success region $S$. There is no universally accepted method
for quantifying replicability and here we do not intend to contribute to the
debate about the most appropriate method. We will simply show the success
regions of different methods, and how the replication sample size can be
computed from them. Some methods depend on the direction of the original effect
estimate $\that_{o}$ and throughout we will assume that it was positive
($\that_{o} > 0$). Functions for computing the probability of replication
success and the required sample size are implemented in the R package
\textbf{BayesRepDesign} (see Appendix) %~\ref{app:package})
for all analysis methods discussed in the following.

@@

We now assume that the one-sided original $p$-value was significant at some
level $\alpha$, \ie{} $p_{o} = 1 - \Phi(\that_{o}/\sigma_{o}) \leq \alpha$.
Replication success at level $\alpha$ % with the two-trials
is then achieved if the replication $p$-value is also significant, \ie{}
$p_{r} = 1 - \Phi(\that_{r}/\sigma_{r}) \leq \alpha$, which implies a success
region
\begin{align*}
  S_{\scriptscriptstyle \text{2TR}}
  = \left[\zalpha\, \sigma_{r}, \infty \right),
\end{align*}
where $\zalpha$ is the $1 - \alpha$ quantile of the standard
normal distribution. The probability of replication success is thus given by
\begin{align}
  \label{eq3:2TRpros}
  \Pr(\that_{r} \in S_{\scriptscriptstyle \text{2TR}} \given \that_{o}, \sigma_{o}, \sigma_{r})
  = % \Phi\left(\frac{\muthatr - \zalpha \, \sigma_{r}}{\sqrt{\sigma^{2}_{r} +
  % \tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right)
  \Phi\left(\frac{\muthatr - \zalpha \, \sigma_{r}}{\sigmathatr}\right)
\end{align}
with $\Phi(\cdot)$ the standard normal cumulative distribution function and
$\muthatr$ and $\sigmathatr$ the mean and standard deviation of the predictive
distribution~\eqref{eq3:fthetar}. %, the latter also depending on $\sigma_{r}$.
Importantly, by decreasing the standard error $\sigma_{r}$ (through increasing
the sample size $n_{r}$), the probability of replication
success~\eqref{eq3:2TRpros} cannot become arbitrarily large but is bounded from
above by
\begin{align}
  \label{eq3:limP2TR}
  \text{limPr}_{\scriptscriptstyle \text{2TR}} =
  \Phi\left(\frac{ \muthatr}{\sqrt{
\tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right).
\end{align}
The required replication standard error $\sigma_{r}^{*}$ to achieve a target
probability of replication success
$1 - \beta < \text{limPr}_{\scriptscriptstyle \text{2TR}}$ can now be obtained
by equating~\eqref{eq3:2TRpros} to $1 - \beta$ and solving for $\sigma_{r}$. This
leads to
\begin{align}
  \label{eq3:ssd2tr}
  \sigma_{r}^{*} =
  \frac{\muthatr \zalpha - \zbeta\sqrt{
  (\zalpha^{2} - \zbeta^{2})\left\{\tau^{2} + (\sigma^{2}_{o} +
  \tau^{2})/(1 + 1/g)\right\} + \muthatr^{2}}}{\zalpha^{2} - \zbeta^{2}}
\end{align}
for $\alpha < \beta$. The standard error $\sigma_{r}^{*}$ can subsequently be
translated in a sample size. The translation depends on the type of effect size,
for instance, for SMD effect sizes we can use the approximation
$n_{r}^{*} \approx 4/(\sigma^*_{r})^{2}$ from
earlier. %Section~\ref{sec3:example}.
Moreover, by assuming a standard error of the form
$\sigma_{r} = \lambda/\sqrt{n_{r}}$ and plugging in the parameters of the
``conditional'' design prior %from Section~\ref{sec3:designpredictive}
($\tau^{2} = 0$, $\mutheta = \that_{o}$, $g \downarrow 0$), we obtain the
well-known sample size formula \citep[ch. 3.3]{Matthews2006}
\begin{align*}
  n_{r}^{*} = \frac{(\zalpha + \zbeta)^{2}}{(\that_{o}/\lambda)^{2}}
\end{align*}
for a one-sided significance test at level $\alpha$ with power $1 - \beta$ to
detect the original effect estimate $\that_{o}$. The formula~\eqref{eq3:ssd2tr}
thus generalizes standard sample size calculation to take into account the
uncertainty of the original estimate, between-study heterogeneity and other
types of external knowledge.

@@

\begin{subappendices}
\renewcommand{\thesection}{\Alph{section}}
\section{The BayesRepDesign R package}
\label{app:package}

@@

    \sigmatheta^{2}}}}_{\to 1} \, \exp\bigg[-\frac{1}{2}\bigg\{\underbrace{

@@

\subsection{The two-trials rule}
\label{sec3sup:2TR}
The two-trials rule is the most common analysis approach for replication
studies. Replication success is declared if both original and replication study
achieve statistical significance at some level $\alpha$ (and both estimates go
in the same direction which can be taken into account by using one-sided
$p$-values). We will study the two-trial under normality using the data model
$\that_{i} \given \theta \sim \Nor(\theta, \sigma^{2}_{i})$ with $\that_{i}$ the
estimate of the unknown effect size $\theta$ from study $i$ and $\sigma_{i}$ is
the corresponding standard error (assumed to be know). The $p$-values for
testing $H_{0} \colon \theta = 0$ versus $H_{1} \colon \theta > 0$ are then
$p_{i} = 1 - \Phi(\that_{i}/\sigma_{i})$ whereas for the alternative
$H_{1} \colon \theta < 0$ they are $p_{i} = \Phi(\that_{i}/\sigma_{i})$. Suppose
the original effect estimate was statistically significant at level $\alpha$,
\ie{} $p_{o} \leq \alpha$. Replication success at level $\alpha$ is then
established if the replication effect estimate $\that_{r}$ is also statistically
significant at level $\alpha$, \ie{} $p_{r} \leq \alpha$. By applying some
algebraic manipulations to the success condition, one can show that this implies
that replication success is achieved if the replication effect estimate
$\that_{r}$ is contained in the success region
\begin{align*}
  S_{\text{2TR}} =
  \begin{cases}
    \left[\zalpha \, \sigma_{r}, \infty \right) & \text{for} ~ \that_{o} > 0 \\
    \left[-\infty, -\zalpha \, \sigma_{r} \right) & \text{for} ~ \that_{o} < 0.
  \end{cases}
\end{align*}

\subsubsection{The multisite two-trials rule}
If multiple replication studies are conducted for one original study (a
\emph{multisite} replication), the two-trials rule is typically modified by
meta-analyzing the effect estimates from all replications and then using the
combined estimate as usual in the two-trials rule \citep[see \eg{} the ``Many
labs'' projects from][]{Klein2014, Klein2018}. Suppose $m$ replication studies
are conducted and produce $m$ effect estimates $\that_{r1}, \dots, \that_{m}$
with standard errors $\sigma_{r1}, \dots, \sigma_{rm}$. Subsequently, a weighted
average
$\hat{\theta}_{r*} = \{\sum_{i = 1}^{m} \hat{\theta}_{ri}/(\sigma^{2}_{ri} + \tau^{2}_{r})\}\,\sigma_{r*}^{2}$
with standard error
$\sigma_{r*} = 1/\surd\{\sum_{i}^{m}1/(\sigma^{2}_{ri} + \tau^{2}_{r})\}$ can be
computed. If the between-replication heterogeneity variance $\tau^{2}_{r}$ is
set to zero this corresponds to the fixed effects estimate of $\theta$, while
estimating $\tau^{2}_{r}$ from the data corresponds to the random effects
estimate. Replication success at level $\alpha$ is then established if the
replication $p$-value is smaller than $\alpha$, \ie{}
$p_{r*} = 1 - \Phi(\that_{r*}/\sigma_{r*}) \leq \alpha$. With some algebra one
can show that this implies a success region for the weighted average replication
effect estimate $\that_{r*}$ given by
\begin{align*}
  S_{\text{2TR}} =
  \begin{cases}
    \left[\zalpha \, \sigma_{r*}, \infty \right) & \text{for} ~ \that_{o} > 0 \\
    \left[-\infty, -\zalpha \, \sigma_{r*} \right) & \text{for} ~ \that_{o} < 0.
  \end{cases}
\end{align*}

@@

\subsection{The replication Bayes factor}
The replication Bayes factor approach uses the replication data $x_{r}$ to
quantify the evidence for the null hypothesis $H_{0}\colon \theta = 0$ relative
to the alternative hypothesis $H_{1} \colon \theta \sim f(\theta \given x_{o})$,
which postulates that the effect size $\theta$ is distributed according to its
posterior distribution based on the original data $x_{o}$. Assume again a normal
model $\that_{i} \given \theta \sim \Nor(\theta, \sigma^{2}_{i})$ with
$\that_{i}$ an estimate of the effect size $\theta$ from study $i \in \{o, r\}$
and $\sigma_{i}$ the corresponding standard error (assumed to be know), and that
we use the alternative $H_{1} \colon \Nor(\that_{o}, \sigma^{2}_{o})$ which
arises from updating an initial flat prior for $\theta$ the original data
$x_{o} = \{\that_{o}, \sigma_{o}\}$. The replication Bayes factor is then
\begin{align}
  \label{eq3sup:bfr}
  \BFr &= \frac{f(\that_{r} \given H_{0})}{f(\that_{r} \given H_{1})}
       = \sqrt{1 + \sigma^{2}_{o}/\sigma^{2}_{r}} \, \exp\left[
         -\frac{1}{2}\left\{ \frac{\that^{2}_{r}}{\sigma^{2}_{r}} -
         \frac{(\that_{r} - \that_{o})^{2}}{\sigma^{2}_{o} + \sigma^{2}_{r}}
         \right\}\right].
\end{align}
Replication success at level $\gamma \in (0, 1)$ is achieved if
$\BFr \leq \gamma$. By applying some algebra to $\BFr \leq \gamma$, one can show
that it is equivalent to the replication effect estimate $\that_{r}$ falling in
the success region
\begin{align*}
  \SBFr
  = \left(-\infty, -\sqrt{A} - (\that_{o}\sigma^{2}_{r})/\sigma^{2}_{o}\right] \bigcup
   \left[\sqrt{A} - (\that_{o}\sigma^{2}_{r})/\sigma^{2}_{o}, \infty\right)
\end{align*}
where
$A = \sigma^{2}_{r}(1 + \sigma^{2}_{r}/\sigma^{2}_{o}) \{\that_{o}^{2}/\sigma^{2}_{o} - 2 \log \gamma + \log(1 + \sigma^{2}_{o}/\sigma^{2}_{r})\}$.

@@

As in the singlesite case, the replication Bayes factor quantifies the evidence
that the data provide for the null hypothesis $H_{0}\colon \theta = 0$ relative
to the alternative hypothesis
$H_{1} \colon \theta \sim \Nor(\that_{o}, \sigma^{2}_{o})$. The marginal density
of the replication data under the null hypothesis is simply
$\bthat_{r} \given H_{0} \sim \Nor_{m}\{0 \, \bone_{m}, \diag(\bsigma^{2} + \tau^{2}_{r} \, \bone_{m}\}$,
whereas the marginal likelihood under the alternative $H_{1}$ is obtained from
integrating the likelihood
% $\bthat_{r} \given \theta \sim \Nor_{m}\{\theta \, \bone_{m}, \diag(\bsigma^{2} + \tau^{2}_{r} \, \bone_{m}\}$
with respect to the prior distribution of $\theta$ under the alternative
$H_{1}$. % $H_{1} \colon \theta \sim \Nor(\that_{o}, \sigma_{o})$.
Let $\Nor(x;m,v)$ denote the normal density function mean $m$ and variance $v$
evaluated at $x$. Define also
$\hat{\theta}_{r*} = \left\{\sum_{i=1}^{n}\hat{\theta}_{ri}/(\sigma^{2}_{ri} + \tau^{2}_{r})\right\} \sigma^{2}_{r*}$
and
$\sigma^{2}_{r*} = 1/\left\{\sum_{i=1}^{n}1/(\sigma^{2}_{ri} + \tau^{2}_{r})\right\}$,
\ie{} the weighted average of the replication effect estimates based on the
heterogeneity $\tau^{2}_{r}$ and its variance. The marginal density is then

\begin{align*}
        f(\hat{\theta}_{r} \given H_{1})
        &= \int f(\hat{\theta}_{r} \given \theta) f(\theta \given H_{1})
                        \, \text{d}\theta \\
              &= \int \frac{\exp\left[-\frac{1}{2} \left\{\sum_{i=1}^{n} \frac{(\hat{\theta}_{ri} - \theta)^{2}}{\sigma^{2}_{ri} + \tau^{2}_{r}} +
                  \frac{(\theta - \that_{o})^{2}}{\sigma^{2}_{o}}\right\} \right]}{
                                    \left\{2\pi \sigma^{2}_{o} \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{1/2}}
    \, \text{d}\theta \\
  &= \int \frac{
    \exp\left[-\frac{1}{2} \left\{\sum_{i=1}^{n} \frac{(\hat{\theta}_{ri} - \hat{\theta}_{r*})^{2}}{\sigma^{2}_{ri} + \tau^{2}_{r}} +  \frac{(\hat{\theta}_{r*} - \theta)^{2}}{\sigma^{2}_{r*}} +
    \frac{(\theta - \that_{o})^{2}}{\sigma^{2}_{o}}\right\} \right]}{
    \left\{2\pi \sigma^{2}_{o} \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{1/2}}
    \, \text{d}\theta \\
  &= \frac{\exp\left[-\frac{1}{2} \left\{\sum_{i=1}^{n} \frac{(\hat{\theta}_{ri} - \hat{\theta}_{r*})^{2}}{\sigma^{2}_{ri} + \tau^{2}_{r}}\right\} \right]}{\left\{2\pi \sigma^{2}_{o} \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{1/2}}
    \underbrace{\int \exp\left[-\frac{1}{2} \left\{\frac{(\hat{\theta}_{r*} - \theta)^{2}}{\sigma^{2}_{r*}} +
    \frac{(\theta - \that_{o})^{2}}{\sigma^{2}_{o}}\right\} \right] \text{d}\theta}_{= \Nor(\hat{\theta}_{r*}; m, \sigma^{2}_{o} + \sigma^{2}_{r*}) 2\pi \sigma_{o} \sigma_{r*}} \\
  &= \left\{(1 + \sigma^{2}_{o}/\sigma^{2}_{r*}) \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{-1/2} \exp\left[-\frac{1}{2}\left\{
    \sum_{i=1}^{n} \frac{(\hat{\theta}_{ri} - \hat{\theta}_{r*})^{2}}{\sigma^{2}_{ri} + \tau^{2}_{r}} + \frac{(\hat{\theta}_{r*} - \that_{o})^{2}}{\sigma^{2}_{r*} + \sigma^{2}_{o}}\right\}\right].
\end{align*}
Dividing the marginal density of $\bthat_{r}$ under $H_{0}$ by the marginal
density of $\bthat_{r}$ under $H_{1}$ leads to cancellation of several terms, and
produces the replication Bayes factor
\begin{align*}
  \BF_{01}(\hat{\theta}_{r})
  &= \frac{f(\hat{\theta}_{r} \given H_{0})}{f(\hat{\theta}_{r} \given H_{1})}
    = \sqrt{1 + \sigma^{2}_{o}/\sigma^{2}_{r*}}  \exp\left[-\frac{1}{2}\left\{
    \frac{\hat{\theta}_{r*}^{2}}{\sigma^{2}_{r*}} -
    \frac{(\hat{\theta}_{r*} - \hat{\theta}_{o})^{2}}{\sigma^{2}_{r*} + \sigma^{2}_{o}}\right\}\right].
\end{align*}
The multisite replication Bayes factor is therefore equivalent to the singlesite
replication Bayes factor from~\eqref{eq3sup:bfr} but using the weighted average
$\that_{r*}$ and its standard error $\sigma_{r*}$ as the replication effect
estimate $\that_{r}$ and standard error $\sigma_{r}$.

@@

%% Bibliography
\bibliographystyle{apalikedoiurl}
\bibliography{bibliography}

>>>>

Taken together, we obtain the design prior
$\theta \given \hat{\theta}_{o}, \sigma^{2}_{o} \sim \Nor(\hat{\theta}_{o}, \sigma^{2}_{o})$
for self-replications and the design prior
$\theta \given \hat{\theta}_{o}, \sigma^{2}_{o} \sim \Nor(\hat{\theta}_{o}, \sigma^{2}_{o} + \tau^{2})$
with $\tau^{2} = 0.05^{2}$ for external-replications. For
example, for the experiment ``Labels'', the design prior would be
centered around the original effect estimate
$\hat{\theta}_{o} = 0.205$ with variance
$\sigma^{2}_{o} = 0.05^{2}$ for a
self-replication, and with variance
\mbox{$\sigma^{2}_{o} + \tau^{2} = 0.05^{2} + 0.05^{2} \approx 0.07^{2}$}
for an external-replication. Figure~\ref{fig3:dpexample} (dark-gray solid lines)
shows the densities of the two priors.
% Note that power
% calculations under the former prior have been termed ``predictive power''
% \citep{Micheloud2020}, while the latter prior has not appeared in the SSD for
% replication studies literature.

@@

\subsection{Probability of replication success and required sample size}
To compute the probability of replication success one needs to select an
analysis method and integrate the predictive distribution~\eqref{eq3:fthetar}
% , respectively, \eqref{eq3:zr}
over the associated success region $S$. There is no universally accepted method
for quantifying replicability and here we do not intend to contribute to the
debate about the most appropriate method. We will simply show the success
regions of different methods, and how the replication sample size can be
computed from them. Some methods depend on the direction of the original effect
estimate $\that_{o}$ and throughout we will assume that it was positive
($\that_{o} > 0$). Functions for computing the probability of replication
success and the required sample size are implemented in the R package
\texttt{BayesRepDesign} (see Appendix~\ref{app3:package}) for all analysis
methods discussed in the following.

@@

We now assume that the one-sided original $p$-value was significant at some
level $\alpha$, \ie{}
\mbox{$p_{o} = 1 - \Phi(\that_{o}/\sigma_{o}) \leq \alpha$}. Replication success
at level $\alpha$ % with the two-trials
is then achieved if the replication \mbox{$p$-value} is also significant, \ie{}
$p_{r} = 1 - \Phi(\that_{r}/\sigma_{r}) \leq \alpha$, which implies a success
region
\begin{align*}
  S_{\scriptscriptstyle \text{2TR}}
  = \left[\zalpha\, \sigma_{r}, \infty \right),
\end{align*}
where $\zalpha$ is the $1 - \alpha$ quantile of the standard
normal distribution. The probability of replication success is thus given by
\begin{align}
  \label{eq3:2TRpros}
  \Pr(\that_{r} \in S_{\scriptscriptstyle \text{2TR}} \given \that_{o}, \sigma_{o}, \sigma_{r})
  = % \Phi\left(\frac{\muthatr - \zalpha \, \sigma_{r}}{\sqrt{\sigma^{2}_{r} +
  % \tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right)
  \Phi\left(\frac{\muthatr - \zalpha \, \sigma_{r}}{\sigmathatr}\right)
\end{align}
with $\Phi(\cdot)$ the standard normal cumulative distribution function and
$\muthatr$ and $\sigmathatr$ the mean and standard deviation of the predictive
distribution~\eqref{eq3:fthetar}. %, the latter also depending on $\sigma_{r}$.
Importantly, by decreasing the standard error $\sigma_{r}$ (through increasing
the sample size $n_{r}$), the probability of replication
success~\eqref{eq3:2TRpros} cannot become arbitrarily large but is bounded from
above by
\begin{align}
  \label{eq3:limP2TR}
  \text{limPr}_{\scriptscriptstyle \text{2TR}} =
  \Phi\left(\frac{ \muthatr}{\sqrt{
\tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right).
\end{align}
The required replication standard error $\sigma_{r}^{*}$ to achieve a target
probability of replication success
$1 - \beta < \text{limPr}_{\scriptscriptstyle \text{2TR}}$ can now be obtained
by equating~\eqref{eq3:2TRpros} to $1 - \beta$ and solving for $\sigma_{r}$. This
leads to
\begin{align}
  \label{eq3:ssd2tr}
  \sigma_{r}^{*} =
  \frac{\muthatr \zalpha - \zbeta\sqrt{
  (\zalpha^{2} - \zbeta^{2})\left\{\tau^{2} + (\sigma^{2}_{o} +
  \tau^{2})/(1 + 1/g)\right\} + \muthatr^{2}}}{\zalpha^{2} - \zbeta^{2}}
\end{align}
for $\alpha < \beta$. The standard error $\sigma_{r}^{*}$ can subsequently be
translated in a sample size. The translation depends on the type of effect size,
for instance, for SMD effect sizes we can use the approximation
$n_{r}^{*} \approx 4/(\sigma^*_{r})^{2}$ from
earlier. %Section~\ref{sec3:example}.
Moreover, by assuming a standard error of the form
$\sigma_{r} = \lambda/\sqrt{n_{r}}$ and plugging in the parameters of the
``conditional'' design prior %from Section~\ref{sec3:designpredictive}
\mbox{($\tau^{2} = 0$, $\mutheta = \that_{o}$, $g \downarrow 0$)}, we obtain the
well-known sample size formula \citep[ch. 3.3]{Matthews2006}
\begin{align*}
  n_{r}^{*} = \frac{(\zalpha + \zbeta)^{2}}{(\that_{o}/\lambda)^{2}}
\end{align*}
for a one-sided significance test at level $\alpha$ with power $1 - \beta$ to
detect the original effect estimate $\that_{o}$. The formula~\eqref{eq3:ssd2tr}
thus generalizes standard sample size calculation to take into account the
uncertainty of the original estimate, between-study heterogeneity and other
types of external knowledge.

@@

\begin{subappendices}
\renewcommand{\thesection}{\Alph{section}}
\section{The BayesRepDesign R package}
\label{app3:package}

@@

    \sigmatheta^{2}}}}_{\to 1} \\
  &\phantom{= \lim_{\sigmatheta^{2} \to \infty}  \int_{0}^{+\infty}} \times \exp\bigg[-\frac{1}{2}\bigg\{\underbrace{

@@

\subsection{The two-trials rule}
\label{sec3sup:2TR}
\sloppy
The two-trials rule is the most common analysis approach for replication
studies. Replication success is declared if both original and replication study
achieve statistical significance at some level $\alpha$ (and both estimates go
in the same direction which can be taken into account by using one-sided
$p$-values). We will study the two-trial under normality using the data model
$\that_{i} \given \theta \sim \Nor(\theta, \sigma^{2}_{i})$ with $\that_{i}$ the
estimate of the unknown effect size $\theta$ from study $i$ and $\sigma_{i}$ is
the corresponding standard error (assumed to be know). The $p$-values for
testing $H_{0} \colon \theta = 0$ versus $H_{1} \colon \theta > 0$ are then
$p_{i} = 1 - \Phi(\that_{i}/\sigma_{i})$ whereas for the alternative
$H_{1} \colon \theta < 0$ they are $p_{i} = \Phi(\that_{i}/\sigma_{i})$. Suppose
the original effect estimate was statistically significant at level $\alpha$,
\ie{} \mbox{$p_{o} \leq \alpha$}. Replication success at level $\alpha$ is then
established if the replication effect estimate $\that_{r}$ is also statistically
significant at level $\alpha$, \ie{} $p_{r} \leq \alpha$. By applying some
algebraic manipulations to the success condition, one can show that this implies
that replication success is achieved if the replication effect estimate
$\that_{r}$ is contained in the success region
\begin{align*}
  S_{\text{2TR}} =
  \begin{cases}
    \left[\zalpha \, \sigma_{r}, \infty \right) & \text{for} ~ \that_{o} > 0 \\
    \left[-\infty, -\zalpha \, \sigma_{r} \right) & \text{for} ~ \that_{o} < 0.
  \end{cases}
\end{align*}

\subsubsection{The multisite two-trials rule}
If multiple replication studies are conducted for one original study (a
\emph{multisite} replication), the two-trials rule is typically modified by
meta-analyzing the effect estimates from all replications and then using the
combined estimate as usual in the two-trials rule \citep[see \eg{} the ``Many
labs'' projects from][]{Klein2014, Klein2018}. Suppose $m$ replication studies
are conducted and produce $m$ effect estimates $\that_{r1}, \dots, \that_{m}$
with standard errors $\sigma_{r1}, \dots, \sigma_{rm}$. Subsequently, a weighted
average
$\hat{\theta}_{r*} = \{\sum_{i = 1}^{m} \hat{\theta}_{ri}/(\sigma^{2}_{ri} + \tau^{2}_{r})\}\,\sigma_{r*}^{2}$
with standard error
\mbox{$\sigma_{r*} = 1/\surd\{\sum_{i}^{m}1/(\sigma^{2}_{ri} + \tau^{2}_{r})\}$}
can be computed. If the between-replication heterogeneity variance
$\tau^{2}_{r}$ is set to zero this corresponds to the fixed effects estimate of
$\theta$, while estimating $\tau^{2}_{r}$ from the data corresponds to the
random effects estimate. Replication success at level $\alpha$ is then
established if the replication $p$-value is smaller than $\alpha$, \ie{}
$p_{r*} = 1 - \Phi(\that_{r*}/\sigma_{r*}) \leq \alpha$. With some algebra one
can show that this implies a success region for the weighted average replication
effect estimate $\that_{r*}$ given by
\begin{align*}
  S_{\text{2TR}} =
  \begin{cases}
    \left[\zalpha \, \sigma_{r*}, \infty \right) & \text{for} ~ \that_{o} > 0 \\
    \left[-\infty, -\zalpha \, \sigma_{r*} \right) & \text{for} ~ \that_{o} < 0.
  \end{cases}
\end{align*}

@@

\subsection{The replication Bayes factor}
The replication Bayes factor approach uses the replication data $x_{r}$ to
quantify the evidence for the null hypothesis $H_{0}\colon \theta = 0$ relative
to the alternative hypothesis
\mbox{$H_{1} \colon \theta \sim f(\theta \given x_{o})$}, which postulates that
the effect size $\theta$ is distributed according to its posterior distribution
based on the original data $x_{o}$. Assume again a normal model
$\that_{i} \given \theta \sim \Nor(\theta, \sigma^{2}_{i})$ with $\that_{i}$ an
estimate of the effect size $\theta$ from study $i \in \{o, r\}$ and
$\sigma_{i}$ the corresponding standard error (assumed to be know), and that we
use the alternative $H_{1} \colon \Nor(\that_{o}, \sigma^{2}_{o})$ which arises
from updating an initial flat prior for $\theta$ the original data
$x_{o} = \{\that_{o}, \sigma_{o}\}$. The replication Bayes factor is then
\begin{align}
  \label{eq3sup:bfr}
  \BFr &= \frac{f(\that_{r} \given H_{0})}{f(\that_{r} \given H_{1})}
       = \sqrt{1 + \sigma^{2}_{o}/\sigma^{2}_{r}} \, \exp\left[
         -\frac{1}{2}\left\{ \frac{\that^{2}_{r}}{\sigma^{2}_{r}} -
         \frac{(\that_{r} - \that_{o})^{2}}{\sigma^{2}_{o} + \sigma^{2}_{r}}
         \right\}\right].
\end{align}
Replication success at level $\gamma \in (0, 1)$ is achieved if
$\BFr \leq \gamma$. By applying some algebra to $\BFr \leq \gamma$, one can show
that it is equivalent to the replication effect estimate $\that_{r}$ falling in
the success region
\begin{align*}
  \SBFr
  = \left(-\infty, -\sqrt{A} - (\that_{o}\sigma^{2}_{r})/\sigma^{2}_{o}\right] \bigcup
   \left[\sqrt{A} - (\that_{o}\sigma^{2}_{r})/\sigma^{2}_{o}, \infty\right)
\end{align*}
where
$A = \sigma^{2}_{r}(1 + \sigma^{2}_{r}/\sigma^{2}_{o}) \{\that_{o}^{2}/\sigma^{2}_{o} - 2 \log \gamma + \log(1 + \sigma^{2}_{o}/\sigma^{2}_{r})\}$.

@@

As in the singlesite case, the replication Bayes factor quantifies the evidence
that the data provide for the null hypothesis $H_{0}\colon \theta = 0$ relative
to the alternative hypothesis
\mbox{$H_{1} \colon \theta \sim \Nor(\that_{o}, \sigma^{2}_{o})$}. The marginal
density of the replication data under the null hypothesis is simply
$\bthat_{r} \given H_{0} \sim \Nor_{m}\{0 \, \bone_{m}, \diag(\bsigma^{2} + \tau^{2}_{r} \, \bone_{m}\}$,
whereas the marginal likelihood under the alternative $H_{1}$ is obtained from
integrating the likelihood
% $\bthat_{r} \given \theta \sim \Nor_{m}\{\theta \, \bone_{m}, \diag(\bsigma^{2} + \tau^{2}_{r} \, \bone_{m}\}$
with respect to the prior distribution of $\theta$ under the alternative
$H_{1}$. % $H_{1} \colon \theta \sim \Nor(\that_{o}, \sigma_{o})$.
Let $\Nor(x;m,v)$ denote the normal density function mean $m$ and variance $v$
evaluated at $x$. Define also
$\hat{\theta}_{r*} = \left\{\sum_{i=1}^{n}\hat{\theta}_{ri}/(\sigma^{2}_{ri} + \tau^{2}_{r})\right\} \sigma^{2}_{r*}$
and
$\sigma^{2}_{r*} = 1/\left\{\sum_{i=1}^{n}1/(\sigma^{2}_{ri} + \tau^{2}_{r})\right\}$,
\ie{} the weighted average of the replication effect estimates based on the
heterogeneity $\tau^{2}_{r}$ and its variance. The marginal density is then

\begin{align*}
        f(\hat{\btheta}_{r} \given H_{1})
        &= \int f(\hat{\btheta}_{r} \given \theta) f(\theta \given H_{1})
                        \, \text{d}\theta \\
              &= \int \frac{\exp\left[-\frac{1}{2} \left\{\sum_{i=1}^{n} \frac{(\hat{\theta}_{ri} - \theta)^{2}}{\sigma^{2}_{ri} + \tau^{2}_{r}} +
                  \frac{(\theta - \that_{o})^{2}}{\sigma^{2}_{o}}\right\} \right]}{
                                    \left\{2\pi \sigma^{2}_{o} \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{1/2}}
    \, \text{d}\theta \\
  &= \int \frac{
    \exp\left[-\frac{1}{2} \left\{\sum_{i=1}^{n} \frac{(\hat{\theta}_{ri} - \hat{\theta}_{r*})^{2}}{\sigma^{2}_{ri} + \tau^{2}_{r}} +  \frac{(\hat{\theta}_{r*} - \theta)^{2}}{\sigma^{2}_{r*}} +
    \frac{(\theta - \that_{o})^{2}}{\sigma^{2}_{o}}\right\} \right]}{
    \left\{2\pi \sigma^{2}_{o} \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{1/2}}
    \, \text{d}\theta \\
  &= \frac{\exp\left[-\frac{1}{2} \left\{\sum_{i=1}^{n} \frac{(\hat{\theta}_{ri} - \hat{\theta}_{r*})^{2}}{\sigma^{2}_{ri} + \tau^{2}_{r}}\right\} \right]}{\left\{2\pi \sigma^{2}_{o} \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{1/2}}
    \underbrace{\int \exp\left[-\frac{1}{2} \left\{\frac{(\hat{\theta}_{r*} - \theta)^{2}}{\sigma^{2}_{r*}} +
    \frac{(\theta - \that_{o})^{2}}{\sigma^{2}_{o}}\right\} \right] \text{d}\theta}_{= \Nor(\hat{\theta}_{r*}; m, \sigma^{2}_{o} + \sigma^{2}_{r*}) 2\pi \sigma_{o} \sigma_{r*}} \\
  &= \left\{(1 + \sigma^{2}_{o}/\sigma^{2}_{r*}) \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{-1/2} \exp\left[-\frac{1}{2}\left\{
    \sum_{i=1}^{n} \frac{(\hat{\theta}_{ri} - \hat{\theta}_{r*})^{2}}{\sigma^{2}_{ri} + \tau^{2}_{r}} + \frac{(\hat{\theta}_{r*} - \that_{o})^{2}}{\sigma^{2}_{r*} + \sigma^{2}_{o}}\right\}\right].
\end{align*}
Dividing the marginal density of $\bthat_{r}$ under $H_{0}$ by the marginal
density of $\bthat_{r}$ under $H_{1}$ leads to cancellation of several terms, and
produces the replication Bayes factor
\begin{align*}
  \BF_{01}(\hat{\btheta}_{r})
  &= \frac{f(\hat{\btheta}_{r} \given H_{0})}{f(\hat{\btheta}_{r} \given H_{1})}
    = \sqrt{1 + \sigma^{2}_{o}/\sigma^{2}_{r*}}  \exp\left[-\frac{1}{2}\left\{
    \frac{\hat{\theta}_{r*}^{2}}{\sigma^{2}_{r*}} -
    \frac{(\hat{\theta}_{r*} - \hat{\theta}_{o})^{2}}{\sigma^{2}_{r*} + \sigma^{2}_{o}}\right\}\right].
\end{align*}
The multisite replication Bayes factor is therefore equivalent to the singlesite
replication Bayes factor from~\eqref{eq3sup:bfr} but using the weighted average
$\that_{r*}$ and its standard error $\sigma_{r*}$ as the replication effect
estimate $\that_{r}$ and standard error $\sigma_{r}$.

@@

%% Bibliography
\newpage
\bibliographystyle{apalikedoiurl}
\bibliography{bibliography}
